```{r, child="_styles.Rmd"}
```

<br>

<h2 id="multi"><b>Version history for `shadia`</b></h2>

The purpose of this page is to provide access to legacy versions of `shadia` that may be needed for ongoing relicensing negotiations that are reliant on older versions of the package (i.e., for model runs that were started before the most recent version on GitHub).

If you are looking for the most recent version, it is always available through the <a href="examples.html">GitHub repo</a>.

<h3 id="multi"><b>Previous versions</b></h3>

`shadia` version 2.0.0 (June 2021): <a href="shadia_1.3.0.tar.gz">shadia_2.0.0.zip</a><br>
`shadia` version 1.8.0 (Sept. 2019): <a href="shadia_1.3.0.tar.gz">shadia_1.8.0.zip</a><br>
`shadia` version 1.3.0 (Aug. 2018): <a href="shadia_1.3.0.tar.gz">shadia_1.3.0.tar.gz</a>

<h3 id="multi"><b>Installation instructions</b></h3>
Installation for older versions is slightly different than for the latest release. You will need to do the following:

1. Download the tarball or binary corresponding to the version you want below. Later versions need to be stored as binaries because the package build is large with river schematics included in documentation.<br>
2. Install the package version from source locally. To do this, you need Rtools installed. Then you can install the package using the following syntax as long as you have set your working directory to the location where the tarball is located:

<br>

<h4 id="multi"><b> Installing from `tar.gz` (tarball)</b></h4>
Here is an example using v 1.3.0. Change the path and version as necessary:
```{r, eval=FALSE, echo=TRUE}
install.packages("path_to_file/shadia_1.3.0.tar.gz",
                 repos=NULL,
                 type="source")
```

Here is another example using devtools from <a href="https://github.com/gregforcey">gregforcey</a> on GitHub:
```{r, eval=FALSE}
devtools::install("path\\to\\shadia-legacy")
```

<h4 id="multi"><b> Installing from `.zip` (binary)</b></h4>
```{r, eval=FALSE, echo=TRUE}
install.packages('path_to_file/shadia_1.8.0.zip', repos = NULL)
```

<br>