```{r, child="../_styles.Rmd"}
```

<h2 id="multi"><b>No passage scenarios</b></h2>

Each of the models in `shadia` can be run under the "no passage" scenario. In other words, by specifying upstream passage probabilities of 0 at the lowermost dam(s) in a given river, the user can simulate a scenario in which there is no fish passage at these or any subsequent dams.

This is easily achieved for any of the models by modifying the default value for the first dam in the system, but can also be done on a dam-by-dam basis.

Here is an example using the Penobscot River, with all other user-specified arguments set to their default values:
```{r, eval=FALSE}
# Run the model without passage at any of the dams
nopass <- penobscotRiverModel(
  upstream = list(milford = 0,
                  howland = 1,
                  westEnfield = 1,
                  brownsMill = 1,
                  moosehead = 1,
                  guilford = 1,
                  weldon = 1)
  )  
```

```{r, eval=TRUE, echo=FALSE}
# Load previously run results - not shown in rmd output
load(file="no_pass.rda")
```

We could then get the output and plot our result. Of course, this is only a single run, so your results may be very different from what is shown here.

```{r}
result = nopass$res

plot(x = result$year, y = result$populationSize,
     type = 'l', lwd=2, col = 'red', xlab='Year',
     ylab='Spawner abundance')
```

The above example would run the model a single time for the default number of years (50, in the case of `penobscotRiverModel()`). If we wanted to do this several hundred times to get outputs that are robust to variability in the input distributions, then we could wrap the call above in a snowfall script.

This might look something like:

```{r, echo=TRUE, eval=FALSE}
# Load R packages
  library(snowfall)
  library(rlecuyer)
  library(shadia)
  library(plyr)

# Initialize parallel mode using sockets
sfInit(parallel=TRUE, cpus=7, type="SOCK")


wrapper <- function(idx) {

  # Run the model
  res1 <- penobscotRiverModel(
          nRuns = 1,
          nYears = 50,
          timing = list(1,1,1,1,1,1,1),
          upstream = list(
            milford = 0,
            howland = 1,
            westEnfield = 1,
            brownsMill = 1,
            moosehead = 1,
            guilford = 1,
            weldon = 1
          ),
          downstream = list(
            stillwater = 1,
            orono = 1,
            milford = 1,
            howland = 1,
            westEnfield = 1,
            brownsMill = 1,
            moosehead = 1,
            guilford = 1,
            weldon = 1
          ),
          pinHarvest = 0,
          inRiverF = 0,
          commercialF = 0,
          bycatchF = 0,
          indirect = 1,
          latent = 1,
          watershed = TRUE
  )
  
  # Define the output lists
    retlist <- list(sim=res1)       
    return(retlist)
}

# Export needed data to workers 
# load required packages on workers.
  sfLibrary(shadia)


# Distribute calculation to workers
  niterations <- 30
  start <- Sys.time()

# Use sfLapply() function to send wrapper() to the workers:
  result <- sfLapply(1:niterations, wrapper) 
    
# Stop snowfall
  Sys.time()-start  
  sfStop()

# 8. Examine the results returned from the cluster:

# 'result' is a list of lists. Save this:
  save(result, file = "sf-no_passage.rda")

# Extract results list from output list
  out <- lapply(result, function(x) x[[c('sim')]])

# Extract user inputs and population metrics
  res <- lapply(out, function(x) x[[c('res')]])
  resdf <- do.call(rbind, res)

# Extract sensitivity variables
  sens <- lapply(out, function(x) x[[c('sens')]])
  sensdf <- do.call(rbind, sens)

# Have a look at result  
  plotter <- ddply(resdf, 'year', summarize,
                   mu=mean(populationSize))
  plot(plotter$year, plotter$mu, type = 'l', col='red', lwd=2,
       xlab = 'Year', ylab='Spawner abundance')
  
```

```{r, echo=FALSE, eval=TRUE}
# Load the result
  load(file="sf-no_passage.rda")
  plot(plotter$year, plotter$mu, type = 'l', col='red', lwd=2,
       xlab = 'Year', ylab='Spawner abundance')
```

<br>